Tsbrowse: a genome browser for Ancestral Recombination Graphs

### 2024-12-12 manuscript/paper.tex
Comment out missing fig

In current practice, simulated ARGs are used as ground-truth to validate
inferences from empirical data
\citep{Kelleher2019,Zhang2023,Speidel2019,Gunnarsson2024.08.31.610248}.
Sophisticated techniques
\citep{Haller2019,Baumdicker2021,Adrion2020,Lauterbur2023} to simulate ARGs
under complex, realistic demographic models \cite{Anderson-Trocmé2023} now
exist. However, models of simulation do not capture \textit{all} the nuances of
population datasets. This results in a clear gap between ARG inference and
application. \texttt{Tsbrowse} captures ARG properties in a model-free way,
providing the means to qualitatively assess inferences. With notable features
of browsability along the genome, scalability and applicability to diverse data
sources, inference and simulation methods, \texttt{tsbrowse} has the potential
to be integrated into biobank-scale data pipelines to improve ARG inference and
analysis.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/SuppFig2.png}
    \caption{\textbf{A view of mutations in the 1000G WGS dataset.} A
screenshot of \texttt{tsbrowse}'s Mutations view for a X Mb region on
chromosome 17 inferred from from 3,202 participants from the 1000 Genomes Whole
Genome Sequencing dataset (1000G) \citep{1000G2015, 1000GWGS}. The genomic
position of the mutations is shown on the X axis, and the age of mutation is
represented on the Y axis. Panel B represents an inference after filtering out
low site-density regions in the samples.}
    \label{fig:Supplementary_Figure_2}
\end{figure}

>>>>

In current practice, simulated ARGs are used as ground-truth to validate
inferences from empirical data
\citep{Kelleher2019,Zhang2023,Speidel2019,Gunnarsson2024.08.31.610248}.
Sophisticated techniques
\citep{Haller2019,Baumdicker2021,Adrion2020,Lauterbur2023} to simulate ARGs
under complex, realistic demographic models \cite{Anderson-Trocme2023} now
exist. However, models of simulation do not capture \textit{all} the nuances of
population datasets. This results in a clear gap between ARG inference and
application. \texttt{Tsbrowse} captures ARG properties in a model-free way,
providing the means to qualitatively assess inferences. With notable features
of browsability along the genome, scalability and applicability to diverse data
sources, inference and simulation methods, \texttt{tsbrowse} has the potential
to be integrated into biobank-scale data pipelines to improve ARG inference and
analysis.

@@

\begin{figure}
    \centering
    % \includegraphics[width=0.95\linewidth]{figures/SuppFig2.png}
    \caption{\textbf{A view of mutations in the 1000G WGS dataset.} A
screenshot of \texttt{tsbrowse}'s Mutations view for a X Mb region on
chromosome 17 inferred from from 3,202 participants from the 1000 Genomes Whole
Genome Sequencing dataset (1000G) \citep{1000G2015, 1000GWGS}. The genomic
position of the mutations is shown on the X axis, and the age of mutation is
represented on the Y axis. Panel B represents an inference after filtering out
low site-density regions in the samples.}
    \label{fig:Supplementary_Figure_2}
\end{figure}
